\ProjectName{}: Data Imputation as a Query Optimization

### 2017-02-22 paper/experiments.tex
paper: minor typos in experiments
fix: use smape instead of rmse

\begin{figure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\columnwidth]{figures/running_times_imputedb.png}
\caption{Query runtimes with \ProjectName{}}
\label{subfig:project-runtime-queries}
\end{subfigure}
~
\begin{subfigure}{\linewidth}
\includegraphics[width=\columnwidth]{figures/running_times_base_tables.png}
\caption{Query runtimes with imputation on base tables}
\label{subfig:base-runtime-queries}
\end{subfigure}
\caption{Comparing \ProjectName{} runtimes for each query (\ref{subfig:project-runtime-queries}) with the runtime for a query when base-table imputations are used (\ref{subfig:base-runtime-queries})}
\end{figure}

@@

Table~\ref{table:rmse} shows the Root-Mean-Squared-Error (RMSE) for \ProjectName{}'s query results when compared to running imputation on the base tables and executing the query on the
cleaned data. Each query was run 10 iterations in both settings and then results from the two approaches were paired up and compared tuple-wise. We average the
squared error across a single query before applying square root. We can see that optimizing for quality indeed reduces the RMSE of query results. In general, the RMSE relative to the
base-imputation approach are acceptable.

\begin{table}
\input{perf_summary.tex}
\caption{Root-Mean-Squared-Error for queries run under different $\alpha$ parameterizations relative to results when imputing on base table}
\label{table:rmse}
\end{table}

@@

\begin{figure}
\begin{lstlisting}
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
\caption{A simple aggregate query on ACS data. Imputing the base table is unfeasible (did not terminate within 20min). \ProjectName's
quality-optimized and performance-optimized query execute in 9 seconds and 1 second, respectively.
}
\label{query-acs}
\end{figure}

>>>>

\begin{figure}
\begin{subfigure}{\linewidth}
\includegraphics[width=\columnwidth]{figures/running_times_imputedb.png}
\caption{Query runtimes with \ProjectName{}}
\label{subfig:project-runtime-queries}
\end{subfigure}
~
\begin{subfigure}{\linewidth}
\includegraphics[width=\columnwidth]{figures/running_times_base_tables.png}
\caption{Query runtimes with imputation on base tables}
\label{subfig:base-runtime-queries}
\end{subfigure}
\caption{Comparing \ProjectName{} runtimes for each query (\ref{subfig:project-runtime-queries}) with the runtime for a query when base-table imputations are used (\ref{subfig:base-runtime-queries})}
\label{fig:runtimes}
\end{figure}

@@

Table~\ref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE) for \ProjectName{}'s query results when compared to 
running imputation on the base tables and executing the query on the
cleaned data. Each query was run 10 iterations in both settings and then results from the two approaches were paired up and compared tuple-wise. We average 
absolute percentage deviations across each iteration of a query, and we report this value averaged over all iterations.
We can see that optimizing for quality indeed reduces the SMAPE of query results. In general, the SMAPE relative to the
base-imputation approach are low in all cases.

\begin{table}
\centering
\input{perf_summary.tex}
\caption{Symmetric-Mean-Absolute-Percentage-Error for queries run under different $\alpha$ parameterizations relative to results when imputing on base table}
\label{table:smape}
\end{table}

@@

\begin{figure}
\begin{lstlisting}
SELECT AVG(c0) FROM acs_dirty;
\end{lstlisting}
\caption{A simple aggregate query on ACS data. Imputing the base table is undesirable (did not terminate within 20min). \ProjectName's
quality-optimized and performance-optimized query execute in 9 seconds and 1 second, respectively.
}
\label{query-acs}
\end{figure}
